---
title: "Visualization with R"
author: "Uche"
date: "8/3/2021"
output:
  pdf_document: default
  html_document: default
---
## Setting up my environment
Notes: loading R packages necessary for visuals.including the "palmer penguins" packages
```{r loading packages}
library(tidyverse)
library(ggplot2)
library(palmerpenguins)
```

## Scatterplot
Trying out different ggplot format for a scatter plot showing relationship between flipper length and body mass
```{r}
ggplot(data = penguins)+ geom_point(mapping = aes(x=flipper_length_mm, y = body_mass_g))
ggplot(data=penguins, mapping = aes(x= flipper_length_mm, y = body_mass_g)) + geom_point()
ggplot(penguins, aes(flipper_length_mm, body_mass_g))+geom_point()
```

## Facet_wrap
Using facet wrap to create multiple chart plots to view each specie seperately
```{r}
ggplot(data = penguins) +
  geom_point(mapping = aes(x = flipper_length_mm, y = body_mass_g, color = species)) + 
  facet_wrap(~species)
```

## facet_grid
```{r}
ggplot(data = penguins)+
  geom_point(mapping = aes(x = flipper_length_mm, y = body_mass_g, color = species)) +
  facet_grid(species~sex)
```

## labels and annotations
Adding titles, subtitles and captions to plots
```{r}
ggplot(data = penguins)+
  geom_point(mapping = aes(x = flipper_length_mm, y = body_mass_g, color = species))+
  labs(title = "Palmer Penguins: Body Mass vs Flipper Length", subtitle = "Sample of Three Penguin Species", caption = "Data collected by Dr. Kristen Gorman")+
  annotate("text", x = 220, y = 3500, label = "The Gentoos are the largest", color = "gold", fontface = "bold")
```

